\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-17 doc/publications/plos16/plos16.tex
standardize and hopefully fix a few citations

After fitting the random forest model and performing the variable importance analysis we hence expect to retrieve these
5 feature in order of the weight that was assigned to them.  We are running Apache Spark 1.6.1 on a YARN cluster with 12
worker nodes each with 16 Intel Xeon E5-2660@2.20GHz CPU cores and 128 GB of RAM.  We captured the OOB 
classification error and the rank-biased-overlap (RBO)
\marginpar{what is wrong with the formatting of this citation?}
\cite[]{Webber.et.al.2010} measure.

@@

We then apply the Mann–Whitney U test to this list to verify that from our list, variants from known BMD loci are ranked
higher than variants from elsewhere in the genome.
We observe a p-value of XXXX, supporting our hypothesis that variants in close proximity to the known BMD genes are
contributing more information to our classification model.

@@

We also frequently see highly-ranked variants in chromosome 22q11. Stagi2010 observe that individuals with a microdeletion
in this region have a significant in bone mass\cite{Stagi2010}. In this same region, we also observe variants present in
PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degredation, and as proposed by Phang et al., proline
is made available by collagen degradation \cite{Phang2008}.

>>>>

After fitting the random forest model and performing the variable importance analysis we hence expect to retrieve these
5 feature in order of the weight that was assigned to them.  We are running Apache Spark 1.6.1 on a YARN cluster with 12
worker nodes each with 16 Intel Xeon E5-2660@2.20GHz CPU cores and 128 GB of RAM.  We captured the OOB 
classification error and the rank-biased-overlap (RBO) \cite{Webber2010} measure.

@@

We then apply the Mann–Whitney U test to this list to verify that from our list, variants from known BMD loci are ranked
higher than variants from elsewhere in the genome.
We observe $P=1.3\times10^{-07}$, supporting our hypothesis that variants in close proximity to the known BMD genes are
contributing more information to our classification model.

@@

We also frequently see highly-ranked variants in chromosome 22q11. Stagi et al. observe that individuals with a microdeletion
in this region have a significant in bone mass\cite{Stagi2010}. In this same region, we also observe variants present in
PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degredation, and as proposed by Phang et al., proline
is made available by collagen degradation \cite{Phang2008}.
